---
title: "Cost of capital, energy adoption and integrated assessment"
subtitle: "Research statement"
description: "Research statement by Ravindu Nawanjana for the Yale School of the Environment PhD programme in Environmental Economics, written with reference to the work of Professor Kenneth Gillingham."
body-classes: statement-page
---

```{r}
#| label: setup
source(file.path(Sys.getenv("QUARTO_PROJECT_DIR", "."), "R", "site.R"))
```

[[Research](../../research.html) / [Statements](../../research.html#statements) / Cost of capital, energy adoption and integrated assessment]{.breadcrumb}

```{r}
statement_header(reference = "Professor Kenneth Gillingham")
```

::: {.prose}
My MSc dissertation at London Metropolitan University asked why climate finance reaches so few of the places that need it. It ended with a theoretical contribution I call the Institutional Reinforcement Cycle (IRC). I want to spend my doctoral years at Yale turning the IRC from a framework I believe in into something a skeptical economist would accept. That means writing it down formally, estimating it, and finding out where it fails.

The IRC treats a climate finance system as a product of its components rather than a sum. Institutional collaboration, policy alignment, blended finance deployment and transparency compound, so a value near zero on one of them can stall the whole system however much capital sits in the funds. My evidence so far is a survey of 103 climate finance professionals and eight interviews with practitioners at UNDP, UNCDF, UN Sustainable Stock Exchanges, FAO, the African Development Bank, the Asian Development Bank, the World Bank GEF, a central bank and a private capital firm. It points to institutional collaboration, rather than the volume of blended finance, as the binding constraint. I presented this at the 3rd International Conference on Biomimicry for Sustainability in August 2026, and the paper is now under revision at Climate and Development. A survey of this size motivates the multiplicative form but does not identify it, and getting to an estimable, identified specification is the first thing I would like to work on with you.

The first direction connects the IRC to integrated assessment modeling, and your recent work, Professor Gillingham, gave me the most to think about here. In your Annual Review of Economics survey with Jesús Fernández-Villaverde and Simon Scheidegger, you note that IAM conclusions depend heavily on parameter values and functional forms. You also describe how deep equilibrium nets make uncertainty quantification feasible on models that were once too costly to solve repeatedly. IAMs typically treat the cost of capital in developing economies as an exogenous parameter. The IRC suggests it is partly an outcome of the institutional architecture around those markets. I would like to estimate that relationship from data and add it to a structural IAM as a regional wedge in the cost of capital. I would then use surrogate model methods to ask how much of the uncertainty in mitigation feasibility for G77 economies traces back to institutional quality rather than to technology or damages. The first year theory and econometrics sequence, and time with your group, are where I intend to build the structural modeling skills this needs.

The second direction is closer to your empirical work on energy technology. My layered capital structure has a concessional first loss tranche, a multilateral guarantee mezzanine and a household deposit senior tranche. It is meant to lower the cost of capital for decentralized clean energy, where financing cost is a large share of the price households face. Your paper with Todd Gerarden, Bryan Bollinger and Daniel Xu on solar tariffs is a model I want to learn from. It finds that a subsidy that does not discriminate by origin beats a targeted one, because each public dollar goes further when it supports lower cost production, and it reaches that result with a structural model disciplined by real data. Your work with Bollinger and Justin Kirkpatrick on valuing solar subsidies sharpens the targeting question. You find implicit discount rates of 15.3 percent for low-wealth households against 10.0 percent for high-wealth ones, and the gap persists even among households with prime credit. That makes the cost of capital one component of the adoption gap, and it gives my structure a clear test. I want to measure how much of that gap a lower cost of capital can close, and what else has to go with it. Dr. Pradeep Kurukulasuriya at UNCDF pressed the same issue from the supply side, with data showing that most multilateral development finance never reaches the highest-risk markets.

There is also a smaller project where carbon credit design meets EV adoption, and I have not found a paper on it. Verra's VM0038 methodology issues credits for electric vehicle charging systems based on the fossil fuel emissions they displace. It ties eligibility and additionality to how far EV adoption has progressed in a market. I worked with this methodology while structuring the carbon programme at Kangara Holdings, where EV charging centres are one component. Your work with Marten Ovaere and Stephanie Weber on carbon policy and the emissions implications of electric vehicles speaks directly to whether such credits measure what they claim to. I would like to ask whether credit rules keyed to market share thresholds distort where charging capacity gets built.

What I bring is field experience and access. In 2025 I wrote Sri Lanka's expression of interest to the Climate Investment Funds' Industry Decarbonization Program, so I have seen from the inside how concessional finance for industry is designed and allocated in a developing economy. Your Science piece with Lint Barrage calls for more economic quantification of industrial decarbonization and industrial policy. A developing country view of concessional finance is where I could contribute to that agenda. I have also sat across the table from rice farmers in Sri Lanka's dry zone while we negotiated an agricultural carbon credit agreement. Before that meeting I had run the additionality test myself with the government, a difference in differences comparison of adopters and nonadopters of the proposed practice changes, checking whether each intervention exceeded VM0042's 5 percent quantitative change threshold and whether regional adoption stayed below the 20 percent common practice ceiling. The farmers were not worried about methodology. They wanted to know what happens to their land rights if the project outlasts the company that signed it. That is a moral hazard and enforcement problem inside blended finance, and I want the tools to model it rather than describe it.

To keep the work tied to data, I plan to run a small pilot with a commercial bank in a Small Island Developing State during the doctorate. My relationships with Dr. Kurukulasuriya, Jason Spensley at the World Bank GEF and Dr. Anthony Miller at UN Sustainable Stock Exchanges make this possible without large seed capital. Their feedback on my early model complicated it usefully. Mr. Spensley, for one, thought the mechanism technically feasible but politically uncertain. The pilot's purpose is to produce real pricing, take-up and default data under a guarantee. I could then use that data to discipline the model's parameters and see where the structure breaks.

This work sits inside a wider programme with three strands, the capital structure itself, its application to energy and its application to regenerative agriculture, which my personal statement describes. I have attended three UNFCCC COPs and two UNCCD COPs, and in those rooms the gap between capital pledged and capital deployed was the most consistent problem I saw. The energy and IAM strands of this programme need the empirical and modeling discipline of your group, Professor Gillingham, and I want to find out early where my framework holds and where it breaks.
:::

```{r}
statement_pager("research/statements/energy-and-integrated-assessment.qmd")
```
