---
title: Code and data
description: "Reproducible research by Ravindu Nawanjana in R, Quarto, Python, Stata and SPSS, covering degree research and applied computational projects on climate finance, carbon markets and agriculture."
toc: true
toc-depth: 2
---

```{r}
#| label: setup
source(file.path(Sys.getenv("QUARTO_PROJECT_DIR", "."), "R", "site.R"))
projects <- read_site("projects")
```

R and Quarto are my main tools for statistics and reporting. I use Python and Jupyter for model engines and as an independent audit layer, and I keep SPSS and Stata files where they are the original evidence.

## Degree research {#degree}

These two repositories reproduce the statistics in my MSc and BSc papers from the survey data. The MSc page on this site reruns the main regression in R and Python each time the site is built, and the [results table](research/multilateral-climate-funds.qmd#results) shows the comparison with the published SPSS values.

```{r}
project_entries("degree")
```

## Applied computational projects {#projects}

```{r}
project_entries("computational")
```

## Tools across the repositories {#tools}

```{r}
#| label: fig-tools
#| fig-cap: "Which tools each public repository uses. Built in R from the same data file as the list above."
#| fig-alt: "Tile chart with nine repositories as rows and seven tools as columns. R appears in five repositories, Python in seven, Quarto in eight, Jupyter in four, and Stata, SPSS and GitHub Actions in one or two each."
#| fig-width: 7.5
#| fig-height: 3.9
tool_levels <- c("R", "Python", "Quarto", "Jupyter", "Stata", "SPSS", "GitHub Actions")
grid <- do.call(rbind, lapply(projects, function(p) data.frame(project = p$name, tool = tool_levels, used = tool_levels %in% p$tools)))
counts <- table(factor(unlist(lapply(projects, `[[`, "tools")), levels = tool_levels))
grid$tool <- factor(grid$tool, levels = tool_levels, labels = paste0(tool_levels, "\n(", counts, ")"))
grid$project <- factor(grid$project, levels = rev(vapply(projects, `[[`, "", "name")))
ggplot(grid, aes(tool, project)) +
  geom_tile(aes(fill = used), colour = "white", linewidth = 1.2) +
  scale_fill_manual(values = c(`TRUE` = site_colours[["leaf"]], `FALSE` = "#eef1ec"), guide = "none") +
  scale_x_discrete(position = "top") +
  labs(x = NULL, y = NULL) +
  theme_site(11) +
  theme(panel.grid = element_blank(), axis.text.x = element_text(size = 9, lineheight = 0.9))
```

## Methods toolkit {#methods}

**Applied quantitative methods.** Linear regression and diagnostics, panel data and fixed effects, difference-in-differences, instrumental variables, regression discontinuity, correlation and reliability analysis, exploratory factor analysis, bootstrapping, survey design, DCF modelling, sensitivity analysis and evidence reconciliation.

**Qualitative methods.** Semi-structured expert interviews, thematic content analysis, policy analysis and institutional mapping.

**Carbon markets and ESG.** Verra AFOLU methodologies VM0042, VM0047 and VM0051, and VM0038 for electric vehicle charging; Project Design Document preparation; additionality assessment; GRI, SASB, TCFD, CDP and SBTi frameworks.

**Software.** R, Python, Quarto, Jupyter, Stata, IBM SPSS Statistics, Git and GitHub Actions. I am also working through IBM Quantum Learning coursework in Qiskit.

## This website {#this-site}

The site is a Quarto project. R reads the content files (news, papers, statements, projects) and writes the pages, draws every chart, and reruns the MSc regression, with a Python check through `reticulate`. The model explorer on the MSc page runs in the browser in Observable JavaScript. A GitHub Actions workflow renders and publishes the site. The source is in the [site repository](https://github.com/RavinduNawanjana/ravindunawanjana.github.io).
