---
title: Research
description: "Papers, research agenda, research statements, writing sample and presentations by Ravindu Nawanjana on climate finance, multilateral climate funds and green finance in emerging markets."
toc: true
toc-depth: 2
---

```{r}
#| label: setup
source(file.path(Sys.getenv("QUARTO_PROJECT_DIR", "."), "R", "site.R"))
```

## Papers {#papers}

```{r}
paper_entries()
```

## Research agenda {#agenda}

My planned dissertation starts from a single instrument, a layered capital structure for climate finance. Concessional grants sit as a standing first-loss tranche rather than a one-off transfer, multilateral guarantees provide mezzanine credit enhancement, and household or bank deposits form the senior tranche. Because the grant and the guarantee absorb losses first, the senior tranche is exposed only to losses beyond them, and with credible guarantees its required return should approach the risk-free rate. That would compress the institutional cost of capital that integrated assessment models treat as exogenous.

The open question is whether that compression survives across different cash flows, from a structured note coupon to a grid tariff to a carbon credit stream, and whether it saves more than the grant costs. The work has three parts. The first formalises the structure as a mechanism design problem. The second applies it to decentralised clean energy, comparing financing terms for guaranteed and unguaranteed grid projects. The third applies it to regenerative agriculture, where carbon-credit-enhanced practices could become investable assets.

## Statements {#statements}

[Written for my application to the PhD programme in Environmental Economics at the Yale School of the Environment (Fall 2027). Each research statement develops the agenda above in conversation with the work of one faculty member.]{.section-intro}

```{r}
statement_list()
```

## Writing sample {#writing-sample}

*Practitioner perspectives on institutional collaboration and multilateral climate funds in the Group of 77 and China.* Extended version of a manuscript under revision at *Climate and Development*, based on my MSc dissertation. 25 pages, including a formal statement of the Institutional Reinforcement Cycle in Appendix A.

[[PDF]](assets/papers/Ravindu_Nawanjana_Writing_Sample.pdf){target="_blank"} &nbsp;|&nbsp; [[Abstract and results]](research/multilateral-climate-funds.qmd)

## Presentations {#presentations}

```{r}
dated_list(read_site("presentations"), "year")
```

UN conference delegations and press coverage are on the [Media](media.qmd) page. Code and data for each project are on the [Code](code.qmd) page.
