---
title: "Statement of purpose"
subtitle: "Why capital sits idle"
description: "Statement of purpose by Ravindu Nawanjana for the Yale School of the Environment PhD programme in Environmental Economics, Fall 2027."
body-classes: statement-page
---

```{r}
#| label: setup
source(file.path(Sys.getenv("QUARTO_PROJECT_DIR", "."), "R", "site.R"))
```

[[Research](../research.html) / [Statements](../research.html#statements) / Statement of purpose]{.breadcrumb}

```{r}
statement_header(kind = "Statement of purpose")
```

::: {.prose}
My paternal grandfather spent his life at sea to put two meals on his family's table. My maternal grandfather farmed paddy with eight children and no means to send my mother past secondary school. I did not inherit their poverty. What I inherited was a question. Why does capital that could change families like mine sit idle, thousands of miles away, in banks that will never lend to them? That question has organized my academic and professional life. It is what I want a PhD to help me answer rigorously.

I began at the edges of it. My BSc thesis at London Metropolitan University tested four drivers of bank green finance adoption (regulation, mechanisms, awareness, and incentives) across emerging-market exchanges; Colombo's own 15-year gap before its first green bond became the clearest example of what a missing driver costs. My MSc thesis moved from a single exchange to the full architecture of multilateral climate finance, using a 103-respondent survey, multiple regression and eight practitioner interviews to analyze blended finance and institutional collaboration among MDBs, central banks, and private capital across the G77 and China. Both projects kept pointing to the same constraint, a shortage of institutions able to move capital toward investments whose returns are slow, uncertain, or politically inconvenient.

That is the puzzle I hope to formalize as a dissertation, though the work will be finding where my framework is wrong. The three hypotheses apply one instrument to different assets. I am engineering a single layered capital structure, with concessional grants held as a standing first-loss tranche instead of a one-off transfer, multilateral guarantees as mezzanine credit enhancement, and household or bank deposits as a senior tranche. Because the grant and the guarantee absorb losses first, the senior tranche is exposed only to losses beyond them. With credible guarantees, its required return should approach the risk-free rate, compressing the institutional cost of capital that integrated assessment models treat as exogenous. The question is whether that compression survives across cash flows, from a structured note coupon to a grid tariff to a carbon credit stream, and whether it saves more than the grant costs.

My first hypothesis is that central-bank-regulated climate deposits should ease two frictions, where guarantees must reveal true risk tolerance and lenders cannot verify project quality. My second extends the logic to energy economics. Anchored guarantees can lower the cost of capital for decentralized green grids, which I would test by comparing financing terms for guaranteed and unguaranteed grid projects. My third turns to regenerative agriculture. Carbon-credit-enhanced practices, held in the structure, can become investable assets across the G77, China, and US rangelands.

The first chapter formalizes the structure as a mechanism design problem; the other two test its predictions in energy and agriculture. As an initial valuation exercise, I have priced an S&P ESG-linked knock-in call embedded in a green structured note using Black-Scholes. Its complete-markets, log-normal assumptions break under climate risk, so I want to extend that valuation to incomplete markets, in Python, R, and Stata.

Over the past year I discussed an early version of this model with Dr. Pradeep Kurukulasuriya, Executive Secretary of UNCDF; Jason Spensley, Senior Climate Change Specialist at the GEF, World Bank Group; and Dr. Anthony Miller, Chief Coordinator of UN Sustainable Stock Exchanges. Dr. Kurukulasuriya pushed me to treat how capital is raised and where it ends up going as linked problems. Mr. Spensley judged the mechanism technically feasible but politically uncertain. Dr. Miller's account of the MDB-financed solar plant near Aswan, closed to Egyptian investors, showed how development finance can bypass local markets. I intend to keep these relationships as a reality check on my designs.

As Head of Impact Investments and Sustainability at Kangara Holdings, I sat across the table from rice farmers in Sri Lanka's dry zone negotiating a carbon credit agreement. I had already run the additionality test with the Sri Lankan government, a difference-in-differences comparison of adopters and non-adopters of recognized regenerative practices, testing each intervention against VM0042's practice-change and common-practice thresholds. My third hypothesis starts from that comparison. But the farmers were not worried about carbon methodology. They wanted to know what would happen to their land rights if the project outlasted the company that signed it. That conversation taught me more about moral hazard and enforcement inside blended finance than any paper I had read. It is what I want to model formally, not intuit, including the residual risk my structure cannot absorb, and who is left holding it.

I hope one of Professors Kenneth Gillingham, Eli Fenichel, or Matthew Kotchen chairs my committee, with the others as members. Professor Gillingham's empirical work on energy technology adoption speaks directly to my second hypothesis, on what market and subsidy design gets households and utilities to adopt decentralized clean energy. Professor Fenichel's dynamic modeling of ecological and economic systems gives me a formal way to treat financial and natural capital as stocks, the weakest part of my framework. Professor Kotchen's research on environmental and public economics, and his multilateral development fund work, sits closest to the mechanism design questions in my first hypothesis. Professor Emeritus Robert Mendelsohn's work valuing climate impacts on agriculture informs my third. I am applying to YSE because I need the hydrology and ecosystem courses it offers, and its applied, policy-facing seminar culture.

My MSc survey surfaced a recurring frustration. The governance of multilateral climate funds is shaped more by donor convenience than recipient need. That is why I am drawn to Yale's Justice, Equity, Diversity, and Sustainability Initiative, whose Research Lab studies funding differences in the environmental sector. I want to ask who receives funding from multilateral climate funds, the accountability question in my dissertation.

Beyond the PhD, I want a career that institutions including UNCDF, GEF, and the World Bank's climate funds call on for mechanism design. I want to move credibly between academic and institutional work. Rigorous ENRE training, grounded in the Economics Department's first-year theory and econometrics sequence, is what will let me do that precisely.
:::

```{r}
statement_pager("research/statement-of-purpose.qmd", root = "../")
```
